---
title: "Homework 1"
author: "Yiming Li"
date: "9/26/2021"
output: github_document
---

## Problem1 

Library the package we need 
```{r}
library(tidyverse)
```

Create dataframe
```{r}
solution_df = tibble(
  vec_numeric = rnorm(10),
  vec_logical = vec_numeric > 0, 
  vec_char =  c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
  vec_factor = factor(c("NY", "NY", "NY", "NY", "CA", "CA", "CA", "FL", "FL", "FL"))
)
```

Calculate mean for each variable
```{r}
numeric_mean = mean(pull(solution_df, var = 1))
logical_mean = mean(pull(solution_df, var = 2))
char_mean = mean(pull(solution_df, var = 3))
factor_mean = mean(pull(solution_df, var = -1))
```
We find mean function works for vec_numeric and vec_logical, and doesn't work for vec_char and vec_factor

Then we use the as.numeric function to variable.
```{r, eval = FALSE}
as.numeric(pull(solution_df, var = 2))
as.numeric(pull(solution_df, var = 3))
as.numeric(pull(solution_df, var = -1))
```
We notice that both logical and factor variable are successfully convert to numeric, but char variable fail. I think the reason is that both logical and factor variable have category while char variable doesn't. But this doesn't explain what happens when we take mean.

## Problem2

Load the penguins dataset:
```{r}
data("penguins", package = "palmerpenguins")
row_size = nrow(penguins)
column_size = ncol(penguins)
modified_penguins = drop_na(penguins, flipper_length_mm)
mean_flipper = mean(pull(modified_penguins, var = 5))
```
Speices variable indicates the speice of penguins, island variable indicates the place penguins lived in, bill_length_mm variable indicates the length of penguin's beak measured in millimeters, bill_depth_mm variable indicates the depth of penguin's beak measured in millimeters, flipper_length_mm variable indicates the length of penguin's front wing measured in millimeters, body_mass_g variable indicates weight of penguin measured in gram, sex variable shows the gender of penguin and year variable shows that when above data were recorded.

The row size for penguins dataframe is `r row_size`, and the column size for penguins dataframe is `r column_size`. The mean of penguins' flipper length is `r mean_flipper`.
