---
title: "Homework 1"
author: "Yiming Li"
date: "9/26/2021"
output: github_document
---

## Problem1 

Library the package we need 
```{r}
library(tidyverse)
```

Create dataframe
```{r}
solution_df = tibble(
  vec_numeric = rnorm(10),
  vec_logical = vec_numeric > 0, 
  vec_char =  c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
  vec_factor = factor(c("NY", "NY", "NY", "NY", "CA", "CA", "CA", "FL", "FL", "FL"))
)
```

Calculate mean for each variable
```{r}
numeric_mean = mean(pull(solution_df, var = 1))
logical_mean = mean(pull(solution_df, var = 2))
char_mean = mean(pull(solution_df, var = 3))
factor_mean = mean(pull(solution_df, var = -1))
```
We find mean function works for vec_numeric and vec_logical, and doesn't work for vec_char and vec_factor

Then we use the as.numeric function to variable.
```{r, eval = FALSE}
as.numeric(pull(solution_df, var = 2))
as.numeric(pull(solution_df, var = 3))
as.numeric(pull(solution_df, var = -1))
mean(as.numeric(pull(solution_df, var = 2)))
mean(as.numeric(pull(solution_df, var = -1)))
```
We notice that both logical and factor variable are successfully convert to numeric, and we can use mean() function on the converted factor variable. But char variable fail to be converted. I think the reason is that both logical and factor variable have category or rank while char variable doesn't. And in my dataframe, the conversion of factor variables into numbers is realized in the order of the letters. 
But difference between conversion doesn't explain what happens when we take mean. I mean that although factor variables can be grouped and sorted, they are non-numerical variables and we can not use mean() function on them. 

## Problem2

Load the penguins dataset:
```{r}
data("penguins", package = "palmerpenguins")
row_size = nrow(penguins)
column_size = ncol(penguins)
modified_penguins = drop_na(penguins, flipper_length_mm)
mean_flipper = mean(pull(modified_penguins, var = 5))
```
Speices variable indicates the speice of penguins, island variable indicates the place penguins lived in, bill_length_mm variable indicates the length of penguin's beak measured in millimeters, bill_depth_mm variable indicates the depth of penguin's beak measured in millimeters, flipper_length_mm variable indicates the length of penguin's front wing measured in millimeters, body_mass_g variable indicates weight of penguin measured in gram, sex variable shows the gender of penguin and year variable shows that when above data were recorded.

The row size for penguins dataframe is `r row_size`, and the column size for penguins dataframe is `r column_size`. The mean of penguins' flipper length is `r mean_flipper`millimeters.

Scatterplot of flipper_length_mm vs bill_length_mm:
```{r}
ggplot(modified_penguins, aes(x = bill_length_mm, y = flipper_length_mm)) + geom_point(aes(color = species))
ggsave("flipper and bill scatterplot.pdf")
```

